A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-25 sections/model_overview/main.tex
Define normal form game explicitly (#40)

In order to define the normal form game the two payoff matrices of the hospitals 
are required. From equation \ref{eq:obj_queueing_systems} the utilities of the
hospitals can be formulated as:

\begin{equation} \label{eq:payoff_entry}
    U_{T_A, T_B}^i = 1 - \left( 
        \hat{P} - P(W_i < t) 
    \right)^2 \quad \textbf{where } i \in \{A, B\}
\end{equation}

@@

\begin{equation} \label{eq:payoff_matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix}, \,
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}
% TODO: Define here the normal form game properly

>>>>

From equation \ref{eq:obj_queueing_systems} the utilities of the
hospitals can be formulated.
The 2-player normal form game between the two hospitals is defined by:
\begin{itemize}
    \item \textbf{Players}: Hospitals \(H_A\) and \(H_B\)
    \item \textbf{Strategy spaces}: \(T_A = \{1, 2, \dots, N_A\}, 
    T_B = \{1, 2, \dots, N_B\}\)
    \item \textbf{Utilities}:    
    \begin{equation} \label{eq:payoff_entry}
        U_{T_A, T_B}^i = 1 - \left( \hat{P} - P(W_i < t) \right)^2 \quad
        \textbf{where } i \in \{A, B\}
    \end{equation}
\end{itemize}

@@

\begin{equation} \label{eq:payoff_matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix}, \,
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}
